On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-17 article/ms.tex

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy. After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work. Current rate estimates of neutron-star mergers imply that should be about $9896$ r-process enhanced stars in the Milky Way, and about $0.087$ in LAMOST DR2. We find that neutron star mergers are also able to create all currently known r-process enhanced stars within a reasonable timescale. Additionally these 47 stars show no correlation to poor metallicity, providing evidence against the relationship of poor metallicity environments and the action of the r-process.
		To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
	\end{abstract}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay. Extremely high neutron densities ($>10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) \citep[e.g.,][]{Burbidge1957,Sneden2008} are necessary for the r-process to occur. Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material. Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material. Using Europium, Reticulum II found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.

@@

	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	However, r-process stars are very rare, which makes finding this stars difficult. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 14 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017}.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of r-process. We provide concluding remarks in Section 4.

@@

	The LAMOST survey is a low resolution optical spectroscopic survey ($R\approx1800$; 3650-9000\,\AA). The second data release from LAMOST \citep{lamost} contains about 2.2 million stellar spectra in the northern sky. Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon}. An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
	The stellar labels used by \textit{The Cannon} included $T_{\rm{eff}}$, $\log{g}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$. For reference, typical uncertainties for these labels are about $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}{g}}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.

@@

	\begin{itemize}
		\item The amplitude of the gaussian profile must be less than $\rm{A}<-0.05$;
		\item The signal to noise (S/N) must be greater than 30;
		\item The deviation from the required wavelength in question must be less than 2 \AA;
		\item The  $\chi_{\rm{r}}^{2}$ value must be less than 3, $\chi_{\rm{r}}^{2}<3$.
		\item All of these conditions must be met for both 4129 \AA\ and 4205 \AA\ for us to consider them sufficiently Eu enhanced.
	\end{itemize}

	These filters produced an initial sample of 62 candidates from the total sample of 454,180. An example candidate is shown in Figure \ref{fig:starindex_423451}. We visually scrutinised each candidate to remove false positives. After this process we were left with 47 likely r-process enhanced candidates, 22 of which stand out as very strong candidates.

@@

	\subsection{Selection effects}
	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.

	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \citet{Barklem2005}. This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process. Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II. However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.

	\subsection{Multiple r-process sites?}
	While it is possible that all currently known r-process enhancements can be made by neutron star mergers (we show this in Section \ref{rates}), we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7). These enhancements imply either that there is more than $1$ active r-process site, or that there is present very heterogeneous levels of mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.

	\subsection{Core-collapse supernovae (CCSN)}
	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.

	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse. In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions. However, how much enhanced material is released from the event is very dependant on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.

	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} . While this may not be a particularly significant amount, core-collapse supernovae occur frequently \citep[$44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.

	\subsection{Neutron star mergers}
	\label{NSmerg}
	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}. However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of $1000\ \rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}. The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.

@@

	\subsection{The rates of r-process events and what they imply}
	\label{rates}
	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}. As well as a reliable estimate of core-collapse supernovae rates from \citet{Li2011}.

	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process giants that should be present in the Milky Way, enhanced both by purely neutron star mergers, and purely core-collapse supernovae. As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way. We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.

	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, $\rm{r=15kpc}$, with a typical IMF and giant star birth rate of approximately $0.3\ $ stars per year. We also assumed the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$. Therefore if we assume a steady-state system, the number of giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the percentage of the Milky Ways stars that our sample represents.

	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance. The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our tracer, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.

	These calculations were achieved by finding a density, $\rho$, such that:
	\begin{center}
	$\rho$ = $M_{Ejecta}*\rm{Rate}*13.8*10^{9}$
	\end{center}
	Where 'Rate' is defined as the number of neutron-star mergers that occur per parsec, per year.

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{center}
	$Eu_{\rm{Mass}} = 47*Eu_{\rm{Atomic\ mass}}*N_{\rm{Eu atoms}}$\\\\
	\end{center}
	Where:
	\begin{center}
	$Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}$ and;\\\\
	$N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}$\\
	\end{center}
	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$

@@

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. These 47 stars represent the first r-process enhanced stars found at [Eu/Fe] $>-2$. They are not clumped in either temperatures, log(g), or radial velocity. They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky. In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale. We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.

@@

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 10,000 r-process enhanced stars in the Milky Way, \todo{and about $0.087$ in LAMOST DR2}. We find that neutron star mergers are able to create all currently known r-process enhanced stars within \todo{X} years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
	Rapid neutron capture occurs when the neutron density is high enough such that the rate of neutron capture will occur faster than the rate at which an isotope undergoes a $\beta$-decay. Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}. Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material. Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of significant contribution by r-process material. Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a core-collapse supernovae event.
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.

@@

	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	However, r-process stars are very rare. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 14 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017}.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of r-process. We provide concluding remarks in Section 4.

@@

	The LAMOST survey is a low resolution optical spectroscopic survey ($R\approx1800$; 3650-9000\,\AA). The second data release from LAMOST \citep{lamost} contains about 2.2 million stellar spectra in the northern sky. Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon}. An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
	The stellar labels included in \textit{The Cannon} model are stellar effective temperature $T_{\rm{eff}}$, surface gravity $\log{g}$, overall metallicity $\rm{[Fe/H]}$, and average relative abundance of elements produced via $\alpha$-particle capture $\rm{[\alpha/Fe]}$. For reference, typical uncertainties for these labels are about $70\,\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\log{g}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.

@@

	\begin{itemize}
		\item The amplitude of the fitted gaussian profile must be less than ${A<-0.05}$;
		\item The signal to noise (S/N) must be greater than 30;
		\item The deviation from the required wavelength in question must be less than 2\,\AA;
		\item The reduced $\chi^{2}$ value must be less than 3, $\chi_r^{2}<3$.
		\item All of these conditions must be met for both 4129\,\AA\ and 4205\,\AA\ for us to consider them sufficiently Eu enhanced.
	\end{itemize}

	These filters produced an initial sample of 62 candidates from the total sample of 454,180. An example candidate is shown in Figure \ref{fig:starindex_423451}. We visually scrutinised each candidate to remove false positives, typically due to data reduction artefacts. After this process we were left with 47 likely r-process enhanced candidates, 22 of which stand out as very strong candidates.

@@

	\subsection{Selection effects}
	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system. The lowest metallicity among the 454,180 giant stars in our sample is $[{\rm Fe/H}] \approx -2.1$. The previous sample of known r-process stars, before this work, exclusively consists of very metal-poor stars with $[{\rm Fe/H}] < -2$ \citep{Barklem2005}. This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at extremely low metallicities of $[{\rm Fe/H}] \lesssim -2.6$ \citep{Simmerer2004} there is a negligible contribution from the s-process
	and all neutron-capture elements must be formed from the r-process. In other words, the primary reason why all r-process enhanced stars have $[{\rm Fe/H}] < -2$ is simply because searches for r-process stars have primarily focussed in the low metallicity regime.

	%Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II. %However, europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.

	\subsection{Multiple r-process sites?}
	While it is possible that all known r-process enhanced stars could be made by neutron star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$). These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.

	\subsection{Core-collapse supernovae}
	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}. Currently, the exact  mechanism that allows material with a high enough neutron density in order to produce  r-process material is unknown.
%	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse. In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions. However, how much enhanced material is released from the event depends heavily on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.

	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004}. While this may not be a particularly significant mass of europium, core-collapse supernovae occur reasonably frequently \citep[44,700$\,\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.

	\subsection{Neutron star mergers}
	\label{NSmerg}
	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}. However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}. The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.

@@

	\subsection{The rates of r-process events and what they imply}
	\label{rates}
	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in Section \ref{NSmerg}. Reliable estimates of core-collapse supernovae are also available \citep{Li2011}. From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron star mergers, or purely by core-collapse supernovae. As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way. We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.

	\todo{1. Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age  of  universe. 2. Calculate  mass of Eu in each 0.8 solar mass star. 3. How many we expect in that 15 kpc sphere throughout universe? 4. Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc. 5. Repeat for CCSN. 6. Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}
	In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3\,stars per year. We considered a spherical volume out to $r_\textrm{GC} = 15\,{\rm kpc}$ from the  centre of the Galaxy. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the percentage of the Milky Ways stars that our sample of r-process  stars represents.

	We assume that a star is said to be enhanced if $[{\rm Eu/Fe}] \geq 0.7$, and assert that all 47 stars here exhibit abundances exceeding this lower-bound. Taking the mass of europium ejected from a neutron star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, this allows us to calculate  a density of europium $\rho_{\rm Eu}$,
\begin{equation}
	\centering
	\rho_{\rm Eu} = M_\textrm{Eu}\frac{dN}{dt}(13.87\times10^9\,{\rm yr})
\end{equation}

\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$).

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{equation}
	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
	\end{equation}
	Where:
	\begin{equation}
	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\\
	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
	\end{equation}
	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$

@@

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. These 47 stars represent the first r-process enhanced stars found at [Fe/H] $>-2$. The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky. We present the first estimate, to our knowledge, that neutron star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe. We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.

@@

		\bibitem[Simmerer et al.(2004)]{Simmerer2004} Simmerer, J., Sneden, C., Cowan, J.~J., et al.\ 2004, \apj, 617, 1091 
